### 2017-05-07 2017mergingmerges/section/03-Definition.tex
Edits to S4

The dynamic execution of process networks consists of three aspects:

\begin{enumerate}
\item \emph{Injection} of a single value from a stream into a process, or a network. Each individual process only needs to accept the value when it is ready for it, and injection into a network succeeds only when they \emph{all} accept it.

@@

% TODO BL: Mention what happens if we choose a different ordering, 
% and how the particular ordering chosen is decided upon.
Importantly, it is the order in which values are \emph{pushed to each particular output channel} which is deterministic, whereas the order in which different processes execute their instructions is not. When we fuse two processes we exploit this fact by choosing one particular instruction ordering that enables the network to advance without requiring unbounded buffering.

@@

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Figure~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The statement $(\ProcInject{p}{v}{c}{p'})$ reads ``given process $p$, injecting value $v$ into channel $c$ yields an updated process $p'$''. The @injects@ form is similar, operating on a network.

@@

Rule (Jump) produces a new label and associated update expressions and rules (CaseT) and (CaseF) evaluate the scrutinee $e$ and emit the appropriate label.

@@

Rule (ProcessInternal) allows an arbitrary process in the network to advance to a new state at any time, provided it does not yield an output action. This allows processes to perform internal computation.
% , without needing to synchronize with the rest of the network.

Rule (ProcessPush) allows an arbitrary process in the network to advance to a new state while yielding an output action $(@push@~c~v)$. For this to succeed it must be possible to inject the output value $v$ into all processes that have channel $c$ as one of their inputs.
% As all consuming processes must accept the output value at the time it is created, there is no need to buffer it further in the producing process. When any process in the network produces an output action we take that as the action of the whole network.

@@

In our system, allowing the execution order of processes to be non-deterministic is critical, as it provides freedom to search for a valid ordering that does not require excessive buffering.
In a direct implementation of concurrent processes using message passing and operating system threads, an actual, working, execution order would be discovered dynamically at runtime. In contrast, the role of our fusion transform is to construct one of these working orders statically. In the fused result process, the instructions will be scheduled so that they run in one of the orders that would have arisen if the network were executed dynamically. In doing so, we also eliminate the need to pass messages between processes --- once they are fused we can just copy values between heap locations.

>>>>

The dynamic execution of a process network consists of:

\begin{enumerate}
\item \emph{Injection} of a single value from a stream into a process, or a network. Each individual process only needs to accept an injected  value when it is ready for it, and injection into a network succeeds only when they \emph{all} processes accept it.

@@

% TODO BL: Mention what happens if we choose a different ordering, 
% and how the particular ordering chosen is decided upon.
Importantly, it is the order in which values are \emph{pushed to each particular output channel} which is deterministic, whereas the order in which different processes execute their instructions is not. When we fuse two processes we choose one particular instruction ordering that enables the network to advance without requiring unbounded buffering. The single ordering is chosen by heuristically deciding which pair of states to merge during fusion, and is discussed in \S\ref{s:EvaluationOrder}.

@@

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Figure~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The statement $(\ProcInject{p}{v}{c}{p'})$ reads ``given process $p$, injecting value $v$ into channel $c$ yields an updated process $p'$''. The @injects@ form is similar, operating on a process network.

@@

Rule (Jump) produces a new label and associated update expressions. Rules (CaseT) and (CaseF) evaluate the scrutinee $e$ and emit the appropriate label.

@@

Rule (ProcessInternal) allows an arbitrary process in the network to advance to a new state at any time, provided it does not yield an output action. This allows processes to perform internal computation.

% , without needing to synchronize with the rest of the network.

Rule (ProcessPush) allows an arbitrary process in the network to advance to a new state while yielding an output action $(@push@~c~v)$. For this to succeed it must be possible to inject the output value $v$ into all processes that have channel $c$ as one of their inputs.

% As all consuming processes must accept the output value at the time it is created, there is no need to buffer it further in the producing process. When any process in the network produces an output action we take that as the action of the whole network.

@@

In our system, allowing the execution order of processes to be non-deterministic is critical, as it provides freedom to search for a valid ordering that does not require unbounded buffering.
In a direct implementation of concurrent processes using message passing and operating system threads, an actual, working, execution order would be discovered dynamically at runtime. In contrast, the role of our fusion transform is to construct one of these working orders statically. In the fused result process, the instructions will be scheduled so that they run in one of the orders that would have arisen if the network were executed dynamically. In doing so, we also eliminate the need to pass messages between processes --- once they are fused we can just copy values between heap locations.
